Fluoroproj: Title to be decided later

### 2023-05-19 manuscript/manuscript_old_with_examp_ref.qmd
manuscript file cleanup

---
title: "Fluoroproj: Title to be decided later"
author: "Stephen D. Shivers, Sophie Fournier, Jakob Stankoski, Jeffrey W. Hollister, Betty J. Kreakie"
abstract: "This is our abstract.  Just seeing how it looks."
format: docx
bibliography: manuscript.bib
---

@@

The goal of this paper is to compare accuracy and precision of a variety of fluorometers with respect to chlorophyll and phycocyanin across a variety of waterbodies as well as with lab grown cultures of green algae and cyanobacteria.

This worked well until the fluorometer gave us problems.

With culture, first look not very linear, but split out but green, cyan, and mixed each grouping shows linear relationship between extracted and in situ turner.  Might not matter that different waterbodies would be in different green/cyano/mix classes.  But the pattern between extracted and in situ/handheld flouros should be similar.  Different pattern with any handheld/in situ would suggest it not perfomring well.

@@

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

@@

@@

Discuss amongst yourselves.

>>>>

---
title: "Fluoroproj: Title to be decided later"
author: "Stephen D. Shivers, Sophie Fournier, Jakob Stankoski, Jeffrey W. Hollister, Betty J. Kreakie"
abstract: "This is our abstract.  Just seeing how it looks."
format: docx
bibliography: manuscript.bib
editor_options: 
  chunk_output_type: console
---

@@

The goal of this paper is to compare accuracy and precision of a variety of fluorometers with respect to chlorophyll and phycocyanin across a variety of waterbodies as well as with lab grown cultures of green algae and cyanobacteria [@Nojavan2019; @Hollister2016].

This worked well until the fluorometer gave us problems [@Hollister2016; @Walsh2017]

With culture, first look not very linear, but split out but green, cyan, and mixed each grouping shows linear relationship between extracted and in situ turner. Might not matter that different waterbodies would be in different green/cyano/mix classes. But the pattern between extracted and in situ/handheld flouros should be similar @Hodges2018. Different pattern with any handheld/in situ would suggest it not perfomring well.

@@

When you click the **Render** button a document will be generated that includes both content and the output of embedded code . You can embed code like this:

@@

![Instrument comparison for Chlorophyll](images/chla_instrument_compare.png){#fig-chla-comparison}

@@

Discuss amongst yourselves. @fig-chla-comparison
